\begin{frame}[allowframebreaks]{Références}
  \footnotesize
  \begin{thebibliography}{99}
    \bibitem[Antigravity]{antigravity}
      Google. \href{https://antigravity.google/docs/browser-subagent}{\emph{Antigravity, Browser Subagent}}, documentation officielle, 2026.
    \bibitem[Playwright]{playwright}
      Microsoft. \href{https://playwright.dev}{\emph{Playwright, End-to-end Testing for Modern Web Apps}}, 2026.
    \bibitem[BrowserStack]{browserstack}
      BrowserStack. \href{https://www.browserstack.com/events}{\emph{QA Leadership Summit 2026, QA Meets AI}}, Mars 2026.
    \bibitem[Chevrot, 2025]{chevrot}
      A. Chevrot \emph{et al.} (Avril 2025).
      \newblock \href{https://arxiv.org/abs/2504.01495}{\emph{Are Autonomous Web Agents Good Testers?}}
      \newblock arXiv:2504.01495 [cs.SE].
    \bibitem[LMArena]{lmarena}
      LMArena. \href{https://lmarena.ai/leaderboard}{\emph{Vision Arena Leaderboard}}, Mars 2026.
    \bibitem[GTT Digital]{gtt_digital}
      GTT. \href{https://www.gtt.fr/digital-solutions}{\emph{Digital Solutions, Smart Shipping}}, 2026.
    \bibitem[Deep Research]{gemini_dr}
      Google. \href{https://blog.google/products/gemini/google-gemini-deep-research/}{\emph{Try Deep Research in Gemini}}, 2024.
    \bibitem[NotebookLM]{notebooklm}
      Google Labs. \href{https://blog.google/technology/ai/notebooklm-google-ai/}{\emph{NotebookLM, an AI-first Notebook}}, 2023.
    \bibitem[Confluence]{confluence}
      Atlassian. \href{https://support.atlassian.com/confluence-cloud/docs/import-content-into-confluence-cloud/}{\emph{Import Content Into Confluence Cloud}}, 2026.
  \end{thebibliography}
\end{frame}
